Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-18 Manuscript Analyses/manuscript_analysis.Rmd
updated pre-post plot

# Customize colors for figures
library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")
my_pal <- lacroix_palette("PeachPear", type = "discrete")

pl_int %>%
  ggplot() +
  aes(x = type,
      y = pwc,
      group = id,
      color = speaker) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  labs(x = "Phase", y = "Intelligibility") +
  theme_classic() +
  scale_color_manual(values = c(my_pal[5], my_pal[6])) +
  theme(legend.position = "none", aspect.ratio = 1)

>>>>

# Customize colors for figures
library(LaCroixColoR) #remotes::install_github("johannesbjork/LaCroixColoR")

my_pal <- c("#782F40", "#B89751")

pl_int %>%
  ggplot() +
  aes(x = type,
      y = pwc,
      group = id,
      color = speaker) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  labs(x = "Phase", y = "Intelligibility") +
  theme_classic() +
  scale_color_manual(values = my_pal) +
  theme(legend.position = "none", aspect.ratio = 1)
